% !TEX encoding = UTF-8 Unicode
%!TEX root = thesis.tex
% !TEX spellcheck = en-US
%%=========================================

\chapter{A geometric model of the rat brain}

This is a section from \citet{Elden2017}, the master thesis about \nameref{chap:vrvis} the VR application this project is loosely inspired by. The section explains how Elden extracted a geometric model of the rat brain from the medical models which is high fidelity volumetric data.

\section*{5.2 Exporting segments of a rat brain atlas as geometry
for the Rat Brain model}
The geometric meshes used for the rat brain model were extracted from
a volumetric and segmented atlas. IKT-SNAP was used to export each
segment of the brain as an STL file. These geometric meshes were then
opened in Blender3
to be converted to OBJ or FBX files. 3DS Max imported
the models and performed all modifications made to the geometry and
structure.
ITK-SNAP requires three files to segment and label the models; the
atlas and a segmentation file, both stored as NII files, and a LABEL file
for the labels. When all files are loaded the program lets the user select a
segment to export and generate a geometric hull along the boundary of the
segment. Due to instability experienced with 3DS Max using all 16 GB of
RAM available on the computer used for development, Blender was used
to first convert the files to FBX files. These FBX files caused no issues when
imported into 3DS Max. Since these meshes were too detailed, they needed
to be reduced and transformed in 3DS Max. The meshes were reduced
such that the entire model consisted of 4.5 million triangles. Most of the
meshes had to be transformed such that each segment was where it should
be inside the model. For some reason the exported meshes were of several
relative scales and heights and a lot of manual work went into moving
and scaling the meshes to match the volumetric model seen in ITK-SNAP.
Properly processed, the model was exported as an FBX file and sent to UE4.
